Earth_microbiome_MS

### 2019-07-15 Earth_microbiome_MS.Rmd
updated

#Read phyloseq object
```{r Pseq read}
#Methods obtained from Callahan et al.

rank_names(githubdata_phyloseq)

@@

>>>>

#Read phyloseq object
```{r Taxonomic filtering}
#Methods obtained from Callahan et al.

#Show taxonomic ranks in the phyloseq object
rank_names(githubdata_phyloseq)

#Create table showing the phyla present in the table 
table(tax_table(githubdata_phyloseq)[, "Phylum"], exclude = NULL)
#It is noted here that some phyla are named following a different denomination system

#Remove unchar

@@

Some of the phyla in the table
